Development of a permanent magnet characterisation framework for use in low-field MRI systems

### 2024-02-28 documentation/colloquium/presentation/index.qmd
a

<p class="">&#x2022; Measure magnets in advance</p>
<p class="">&#x2022; Execute optimization or sorting algorithms on the magnet field data</p>
<p class="">&#x2022; Build an optimized magnet</p>

<hr>

::: {.container}
:::: {.col}
<h4 style="text-align: center;">BUT</h4>
::::
:::

<hr>

<p class="fragment">&#x2022; Existing projects follow this approach but only implement individual parts</p>
<p class="fragment">&#x2022; Incompatible data-formats</p>
<p class="fragment">&#x2022; Complex magnetic field sensor integrations</p>
<p class="fragment">&#x2022; Usage of non open source software</p>
<aside class="notes">
* diverse projekte welche einzelne algrothmen dazu haben
* jedoch nicht kompatible zueinander

>>>>

## But

<p class="fragment">&#x2022; Existing projects follow this approach but only implement individual parts</p>
<p class="fragment">&#x2022; Incompatible data-formats</p>
<p class="fragment">&#x2022; Complex magnetic field sensor integrations</p>
<p class="fragment">&#x2022; Usage of non open source software</p>
